Measurement of total hadronic differential cross sections in the LArIAT experiment

### 2018-04-27 Chapter-9/9-Uncertainty.tex
s

\subsection{Uncertainty on $E_{loss}$}
We estimate the uncertainty on the energy loss between the beamline momentum measurement and the TPC, $E_{loss}$, using the DDMC pion sample. We shoot pions from WC4 with the same momentum distribution as in the beamline data and plot the true $E_{loss}$ for that sample. The width of the $E_{loss}$ distribution is the $\delta E_{loss}$.

>>>>

\subsection{$E_{loss}$}
We derive an estimate of the energy loss between the beamline momentum measurement and the TPC ($E_{loss}$) from the Monte Carlo using the DDMC pion sample, since this quantity is not  measurable directly on data. We shoot pions from WC4 with the same momentum distribution as in the beamline data and plot the true $E_{loss}$ for that sample. The $E_{loss}$ distribution for the 60A  and 100A pion sample is shown in figure \ref{fig:ELoss60A}, left and right respectively. A clear double peaked structure is visible, which is due to the particles either missing or hitting the HALO paddle: a schematic rendering of this occurrence is  shown in figure \ref{fig:Halo}. The kinematic at WC4 determine the trajectory of a particle and whether or not it will hit the halo paddle. Thus, to

\begin{figure}[hbpt]
\centering
\includegraphics[width=0.45\textwidth]{Chapter-9/Images/E_loss60A.png}
\includegraphics[width=0.45\textwidth]{Chapter-9/Images/E_loss100A.png}
\caption{True energy loss between WC4 and the TPC front face according to the MC simulation of the 60A runs (left) and of the 100A runs (right).}
\label{fig:ELoss60A}
\end{figure}

\begin{figure}[hbpt]
\centering
\includegraphics[scale=0.5]{Chapter-9/Images/Halo.png}
\caption{Schematic rendering of the particle path between WC4 and the TPC front face. The paddle with the hollow central circle represents the Halo paddle. We illustrate two possible trajectories: in black, a trajectory that miss the paddle and goes through the hole in the Halo, in blue a trajectory that hits the Halo paddle and goes through the scintillation material.}
\label{fig:Halo}
\end{figure}

The width of the $E_{loss}$ distribution is the $\delta E_{loss}$.
